---
title: "P09_Cacace_Notebook_R"
author: "Nikita Cacace"
date: "23/09/2021"
output:
  html_document: default
  pdf_document: 
    toc: yes
    fig_width: 3
    fig_height: 2
    fig_caption: yes
    number_sections: yes
editor_options: 
  markdown: 
    wrap: 72
---
##Packages and options:
```{r}
library(readr)
library(tidyr)
library(dplyr)
options(digits = 3)
```

##Data import:
```{r}
Dispo_Alim_df <- read_csv("C:/Users/leroc/Dropbox/2020 - 2021 OpenClassrooms, MOOC et conférences/09 - Produisez une étude de marché avec R ou Python/DisponibiliteAlimentaire_2017.csv")
Pop_df <- read_csv("C:/Users/leroc/Dropbox/2020 - 2021 OpenClassrooms, MOOC et conférences/09 - Produisez une étude de marché avec R ou Python/Population_2000_2018.csv")
Pib_df <- read_csv("C:/Users/leroc/Dropbox/2020 - 2021 OpenClassrooms, MOOC et conférences/09 - Produisez une étude de marché avec R ou Python/Population_2000_2018.csv")
```
## Colums renaming:
```{r}
names(Dispo_Alim_df)[1] <- "c_domain"
names(Dispo_Alim_df)[2] <-"domain"
names(Dispo_Alim_df)[3] <-"c_zone"
names(Dispo_Alim_df)[4] <-"zone"
names(Dispo_Alim_df)[5] <-"c_element"
names(Dispo_Alim_df)[6] <-"element"
names(Dispo_Alim_df)[7] <-"c_prod"
names(Dispo_Alim_df)[8] <-"prod"
names(Dispo_Alim_df)[9] <-"c_year"
names(Dispo_Alim_df)[10] <-"year"
names(Dispo_Alim_df)[11] <-"unit"
names(Dispo_Alim_df)[12] <-"value"
names(Dispo_Alim_df)[13] <-"symb"
names(Dispo_Alim_df)[14] <-"symb_description"

names(Pop_df)[1] <- "c_domain"
names(Pop_df)[2] <-"domain"
names(Pop_df)[3] <-"c_zone"
names(Pop_df)[4] <-"zone"
names(Pop_df)[5] <-"c_element"
names(Pop_df)[6] <-"element"
names(Pop_df)[7] <-"c_prod"
names(Pop_df)[8] <-"prod"
names(Pop_df)[9] <-"c_year"
names(Pop_df)[10] <-"year"
names(Pop_df)[11] <-"unit"
names(Pop_df)[12] <-"value"
names(Pop_df)[13] <-"symb"
names(Pop_df)[14] <-"symb_description"
names(Pop_df)[15] <-"note"

names(Pib_df)[1] <- "c_domain"
names(Pib_df)[2] <-"domain"
names(Pib_df)[3] <-"c_zone"
names(Pib_df)[4] <-"zone"
names(Pib_df)[5] <-"c_element"
names(Pib_df)[6] <-"element"
names(Pib_df)[7] <-"c_prod"
names(Pib_df)[8] <-"prod"
names(Pib_df)[9] <-"c_year"
names(Pib_df)[10] <-"year"
names(Pib_df)[11] <-"unit"
names(Pib_df)[12] <-"value"
names(Pib_df)[13] <-"symb"
names(Pib_df)[14] <-"symb_description"
names(Pib_df)[15] <-"note"
```

##Data cleaning:
#Dispo_Alim_df:
```{r}
mode(Dispo_Alim_df)
```
Dispo_Alim_df is a 'list' we want a data frame
```{r}
as.data.frame(Dispo_Alim_df,
              row.names = NULL, 
              optional = FALSE,
              cut.names = FALSE,
              col.names = names(x), 
              fix.empty.names = TRUE,
              stringsAsFactors = default.stringsAsFactors())
str(Dispo_Alim_df)
summary(Dispo_Alim_df)
sum(is.na(Dispo_Alim_df))
```
The number of lines and columns is as expected. There are no missing values nor NA."code" columns should be in chr and not in num.
```{r}
Dispo_Alim_df$c_domain <- as.character(Dispo_Alim_df$c_domain)
Dispo_Alim_df$c_zone<- as.character(Dispo_Alim_df$c_zone)
Dispo_Alim_df$c_element<- as.character(Dispo_Alim_df$c_element)
Dispo_Alim_df$c_prod<- as.character(Dispo_Alim_df$c_prod)
Dispo_Alim_df$c_year <- as.character(Dispo_Alim_df$c_year)

summary(Dispo_Alim_df)
```

#Pop_df:
```{r}
mode(Pop_df)
```
Pop_df is a 'list' we want a data frame
```{r}
as.data.frame(Pop_df,
              row.names = NULL, 
              optional = FALSE,
              cut.names = FALSE,
              col.names = names(x), 
              fix.empty.names = TRUE,
              stringsAsFactors = default.stringsAsFactors())
str(Pop_df)
summary(Pop_df)
sum(is.na(Pop_df))
```
The number of lines and columns is as expected.No missing data except for "note", it may be deleted latter. ''code'' are not in chr.

```{r}
Pop_df$c_domain <- as.character(Pop_df$c_domain)
Pop_df$c_zone<- as.character(Pop_df$c_zone)
Pop_df$c_element<- as.character(Pop_df$c_element)
Pop_df$c_prod<- as.character(Pop_df$c_prod)
Pop_df$c_year <- as.character(Pop_df$c_year)

summary(Pop_df)
```

#Pib_df:
```{r}
mode(Pib_df)
```
Pib_df is a 'list' we want a data frame
```{r}
as.data.frame(Pib_df,
              row.names = NULL, 
              optional = FALSE,
              cut.names = FALSE,
              col.names = names(x), 
              fix.empty.names = TRUE,
              stringsAsFactors = default.stringsAsFactors())
str(Pib_df)
summary(Pib_df)
sum(is.na(Pib_df))
```
The number of lines and columns is as expected.No missing data except for "note", it may be deleted latter. ''code'' are not in chr.

```{r}
Pib_df$c_domain <- as.character(Pib_df$c_domain)
Pib_df$c_zone<- as.character(Pib_df$c_zone)
Pib_df$c_element<- as.character(Pib_df$c_element)
Pib_df$c_prod<- as.character(Pib_df$c_prod)
Pib_df$c_year <- as.character(Pib_df$c_year)

summary(Pib_df)
```
